\begin{acknowledgments}

  As I conclude my thesis, I am profoundly grateful for the invaluable support and
  guidance I have received from numerous individuals who have made my academic
  journey possible.

  First and foremost, I owe my deepest thanks to Professor Alexandre Jesus and
  Carlos Fonseca, my supervisors, for their unwavering support, constant
  encouragement, and unwavering inspiration throughout my academic journey. They
  have consistently made time to listen to my challenges and provided assistance
  whenever needed. Most importantly, I deeply appreciate their mentorship and the
  friendship that has helped me develop both technically and personally.

  I extend my heartfelt gratitude to my~\textquote{university family}, particularly my
  \textquote{goddaughters}, who have shown me care and support when I needed it most. Each
  one of you has made a meaningful contribution to my days. I want to specifically
  thank Tatiana Almeida for her constant check-ins, Inês Marçal for sharing jokes
  and bringing laughter into my life, and Joana Antunes for her friendly waves in
  the DEI corridor whenever I filled my water bottle. Additionally, I want to
  express my gratitude to my~\textquote{grandson}, João Moreira, for being a constant presence
  during late-night visits to my dorm room, patiently listening to my vents and
  discussing our days. Your kindness and companionship have meant the world to me.

  I extend my thanks to all my friends who have been by my side throughout this
  journey. Although it is impossible to mention each one of you, please know that
  this work would not have been possible without your unwavering support. In
  particular, I would like to express my gratitude to Samuel Carinhas, my
  \textquote{wingman} in all our adventures, gaming nights, and other memorable moments. To Duarte
  Dias, Gabriel Fernandes, and Miguel Rabuge, your great discussions,
  collaborative project work, and cherished moments have made this journey so
  enjoyable. Mariana Loreto and André Silva, thank you for having faith in me,
  sometimes more than I did, and for always encouraging me to give my best.

  I must also extend special thanks to all the members of the Algorithms and
  Optimization Laboratory with whom I have shared countless moments and from whom
  I have learned invaluable lessons. I'm especially grateful to Luis Paquete for
  setting me on my research path and to Gonçalo Lopes for always keeping me
  company in the lab during lunch or over coffee. I also want to acknowledge the
  members of the Núcleo de Estudantes de Informática, who have made this year an
  unforgettable and pleasant experience.

  My gratitude also goes to my uncle (and godfather) Rui Duque and aunt Andreia
  Rosa for always being present, offering valuable advice, and helping me take a
  break when I needed it most.

  Last but certainly not least, none of this would have been possible without the
  unwavering support of my sister and my parents. They have always been there to
  provide for me, teach me, and support me in every way possible, and to them, I
  owe everything.

\end{acknowledgments}